\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-29 latex/paper_sensores/paper.tex
mi parte del paper

It is interesting to compare the values obtained with the theoretical values of each parameter. As we can see, comparing the vector obtained with the seed, the values of the gains and the rotations are similar to what is declared in the datasheets. However the offset values obtained differ considerably from the information of the datasheet (see \cite{bib:acc_data}), where is declared that the 0g output deviation from ideal is $\pm 35 mg$ for axes $x$ and $y$ and $\pm 40mg$ for axis $z$. This means that the offsets should be less than $11$ bits.\\

@@

At first appearence it does not seems right that the accuracy of the results is comparable with the instrument resultion. However, this fact can be explain because the effect of electrical noise. Let's supose that the true acceleration correspond to $128.2$ bits. If the accelerometer was ideal a constant lecture of $128$ bits would be obtained. However, due to the electrical noise the value of the measure obtained varies typically one or two bits (see Figure \refp{fig:noise}). Those variations are not uniform, on the contrary: they depend on the true value of the acceleration. In the considered case the value $128$ will be more commun that the value $129$, yet if the true acceleration correspond to $128.74$ bits, the opposite would happen. To sum up, the electrical noise behaves in a way that depe0nds on the true value of the acceleration. Thus, taking an average of almost $20000$ samples per measure ($20$ seconds of data), the obtained value is more accurate than the reslution of the instrument is obtained.

\subsection{Temperature adjust}

>>>>

It is interesting to compare the values obtained with the theoretical values of each parameter. As we can see, comparing the vector obtained with the seed, the values of the gains and the rotations are similar to what is declared in the datasheets. However the offset values obtained differ considerably from the information of the datasheet (see \cite{bib:acc_data}), where is declared that the 0g output deviation from ideal is $\pm 35 mg$ for axes $x$ and $y$ and $\pm 40mg$ for axis $z$. This means that the offsets should be less than $11$ bits, therefore a difference between the results obtained in the calibration and what is stated in the datasheet of the sensor exists.\\

@@

At first appearence it does not seems right that the accuracy of the results is comparable with the instrument resultion. However, this fact can be explain because the effect of electrical noise. Let's supose that the true acceleration correspond to $128.2$ bits. If the accelerometer was ideal a constant lecture of $128$ bits would be obtained. However, due to the electrical noise the value of the measure obtained varies typically one or two bits (see Figure \refp{fig:noise}). Those variations are not uniform, on the contrary, they depend on the true value of the acceleration. In the considered case the value $128$ will be more commun that the value $129$, yet if the true acceleration correspond to $128.74$ bits, the opposite would happen. To sum up, the electrical noise behaves in a way that depe0nds on the true value of the acceleration. Thus, taking an average of almost $20000$ samples per measure ($20$ seconds of data), the obtained value is more accurate than the reslution of the instrument is obtained. \\

\subsubsection{Gyroscope}
For the gyroscope the vector of parameters obtained is the following:

\begin{equation}
\boldsymbol{\theta}_\omega = \begin{array}{c}
[792.44,\, 808.61, \, 799.44, \, -33.52,  \\
-31.41, \, -1.07, \, 0.02, \, 0.06, \\
 -1.32 \times 10^{-3}, \,  2.59\times 10^{2}, \,  -3.25 \times 10^{-2} \, 6.07\times 10^{-1}
 \end{array}]^T
\end{equation}

As we can see the gains are very similar to the ones that are declared on the datasheets. The maximum relative error obtained is:

\begin{equation}
\varepsilon_{\omega gain} = \frac{|823.63 - 792.44|}{823.63} = 3.8 \%
\end{equation}

On the other hand, the typical offset error is $\pm 40 ^\circ s^{-1}$
\subsection{Temperature adjust}
